---
title: "Investigating the impact of lockdown on lifestyle "
author: "SID1 SID2 SID3 SI4 SID5"
subtitle: "Subject Matter"
date: "University of Sydney | Day Month 2021"
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

<br>

# Executive Summary



<br>

# Full Report


## Initial Data Analysis (IDA)

```{r}
# LOAD DATA
survey1 = read.csv("DATA1001-survey-altered.csv")
#str(survey)

library(tidyverse)

survey_fresh = survey1 %>%
                    rename(
                      `Age` = 2,
                      `LGA` = 3,
                      `Opinion on lockdown` = 4,
                      `Following rules` = 5,
                      `Cohabitation` = 6,
                      `Income` = 7,
                      `Lockdown time outdoors` = 8, 
                      `Lockdown time exercising` = 9,
                      `Exercise hours` = 10,
                      `Low mood` = 11,
                      `Happy mood` = 12,
                      `Hours technology` = 13
                       )

head(survey_fresh, 5)
tail(survey_fresh, 5)
str(survey_fresh)

opinionvsrule <- data.frame(x = survey_fresh$`Opinion on lockdown`, y = survey_fresh$`Following rules`)
library(ggplot2)
library(wesanderson)

#Defining x and y 
ggplot(opinionvsrule, aes(x,y))+
  geom_point()

#models
## linear
model_linear <- lm(y~x, data=opinionvsrule)

# plotting
##basic linear
ggplot(opinionvsrule , aes(x, y)) +
  geom_point() +
  geom_line(y = predict(model_linear))

##loess
library(wesanderson)
gb <- wes_palette("GrandBudapest1")
ggplot(opinionvsrule, aes(x, y)) +
  geom_point() +
  geom_smooth(method="loess",colour = "green")

ggplot(opinionvsrule, aes(x, y)) +
  geom_point(colour = "blue") +
  geom_smooth(method="lm",colour = "green")
  
#facet_grid(survey_fresh$`Lockdown time outdoors`)



``` 
```{r}
# x and y values
opvshap <- data.frame(x = survey_fresh$`Opinion on lockdown`, y = survey_fresh$`Happy mood`)

#plot

ggplot(opvshap, aes(x, y)) +
  geom_point() +
  geom_smooth(method="lm",colour = "green")

#Negative correlation!!! less exercise equates to higher average days feeling low
# x and y values
exvslow <- data.frame(x = survey_fresh$`Exercise hours`, y = survey_fresh$`Low mood`)

#plot

ggplot(exvslow, aes(x, y)) +
  geom_point() +
  geom_smooth(method="lm",colour = "green")

#in reverse
# x and y values
lowvsex <- data.frame(x = survey_fresh$`Low mood`, y = survey_fresh$`Exercise hours`)

#plot

ggplot(lowvsex, aes(x, y)) +
  geom_point() +
  geom_smooth(method="lm",colour = "green")

#happy mood and time outdoors

outvshap <- data.frame(x = survey_fresh$`Happy mood`, y = survey_fresh$`Exercise hours`)

ggplot(outvshap, aes(x,y, colour = survey_fresh$LGA))+
  geom_point(aes(fill = survey_fresh$LGA)) +
  geom_smooth(method= "lm", colour = "green")

#plot

```
```{r}
```
## Summary:

## Source:
Data was collected via a google forms survey active between (add dates)

## Structure:
- brief summary of variable and types of data collected (e.g numeric/factor ect)


## Research Question(s)

<br>

## Articles

<br>

## References
Use APA

<br>

## Acknowledgments
When did you team meet (date and time), and what did each team member contribute?



